%-------------------------
% Resume in Latex
% Author : Abey George (template)
% Updated for: Yash Dixit (Backend + DevOps + Platform)
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usetikzlibrary{svg.path}

\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Adjust margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.7in}
\addtolength{\textwidth}{1.4in}
\addtolength{\topmargin}{-.8in}
\addtolength{\textheight}{1.6in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands (clean spacing + consistent bullets)
\newcommand{\resumeItem}[1]{
  \item \small{#1}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-2pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-1pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}, topsep=2pt, itemsep=2pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[topsep=2pt, itemsep=2pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{1pt}}

\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Yash Dixit} \\ \vspace{2pt}
    Ajmer, Rajasthan \\ \vspace{2pt}
    \small
    \href{tel:+916376037064}{\underline{+91-6376037064}} ~
    \href{mailto:yashdixit921@gmail.com}{\underline{yashdixit921@gmail.com}} ~
    \href{https://linkedin.com/in/yash-dixit-26bbb5167/}{\underline{linkedin.com/in/yash-dixit-26bbb5167}} ~
    \href{https://github.com/yash921}{\underline{github.com/yash921}} ~
    \href{https://leetcode.com/yash921/}{\underline{leetcode.com/yash921}}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
Software Engineer with 4.5+ years of experience across Python backend development, DevOps, and cloud infrastructure. Specialized in building scalable REST APIs, event-driven systems, and enterprise data-ingestion pipelines on AWS and Kubernetes. Proven production ownership across reliability, observability, CI/CD automation, and infrastructure-as-code—delivering platforms that improve scalability, onboarding speed, and operational efficiency.

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}, topsep=2pt, itemsep=2pt]
\small{\item{
\textbf{Languages:} Python, Go, Groovy, Shell Script, SQL \\
\textbf{Backend \& Data:} REST APIs, Microservices, Event-Driven Architecture, Webhooks, Apache Airflow \\
\textbf{Cloud \& DevOps:} AWS (EKS, ECS Fargate, EC2, Lambda, Kinesis, S3, SQS, IAM, VPC, CloudWatch, Redshift), Docker, Kubernetes, Terraform, CloudFormation, Jenkins, GitHub Actions, ArgoCD, Helm, Ansible, CI/CD \\
\textbf{Databases \& Search:} PostgreSQL, OpenSearch, Elasticsearch, Redis \\
\textbf{Observability \& Security:} Grafana, Prometheus, OpenSearch Logs, Trivy Security Scanning
}}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}

\resumeSubHeadingListStart
\resumeSubheading
{Workato}{June 2025 -- Present}
{Software Engineer — Backend \& Platform (Enterprise Search / GO Team)}{Remote, India}
\resumeItemListStart
\resumeItem{Joined Workato Core AI Team; owned backend services, ingestion pipelines, and platform integrations for Enterprise Search (GO).}
\resumeItem{Drove architecture discussions and engineering reviews, authored design documents, and coordinated cross-functionally with infrastructure and product teams to align technical execution with business priorities.}
\resumeItem{Migrated user search and history processing from synchronous execution to an event-driven architecture using AWS Kinesis and Apache Airflow, decoupling OpenSearch indexing from core services.}
\resumeItem{Built pre-crawl connectivity test APIs for major datasources (Confluence, Salesforce, Slack, Highspot, Jira, Zendesk, Google Drive), reducing failed crawls and accelerating customer onboarding by 40\%.}
\resumeItem{Implemented scalable crawler strategies (parallel user-based Google Drive crawling, shared drive discovery, incremental indexing) using Airflow for enterprise-scale ingestion.}
\resumeItem{Improved observability via structured error codes, failure notifications, and real-time crawl status webhooks; streamed auth errors, API failures, and crawl logs back to the Workato platform for faster triage.}
\resumeItem{Partnered with infra teams to migrate the platform from ECS to EKS, centralize logging via Quickwit, and establish a staging environment mirroring production for safer releases.}
\resumeItem{Debugged and resolved production connector issues (auth, permissions, API limits, data access) to unblock customer onboarding and stabilize enterprise deployments.}
\resumeItem{\textbf{Tech Stack:} Python, RAG, AWS (EKS/ECS, Kinesis), Apache Airflow, OpenSearch, REST APIs}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
{Workato}{Oct 2024 -- June 2025}
{Field Infrastructure Engineer}{Remote, India}
\resumeItemListStart
\resumeItem{Built self-serve cloud provisioning automation across AWS/Azure/GCP using Workato workflows + GitHub Actions + Terraform (EC2, RDS, S3, SQS, Redshift, Bedrock), enabling end-to-end lifecycle management.}
\resumeItem{Implemented automated resource expiry notifications and deletion workflows using Terraform state, improving governance and reducing orphaned infrastructure.}
\resumeItem{Deployed internal products on AWS ECS Fargate; implemented CI/CD pipelines for Dev/Prod with rolling deployments to achieve zero-downtime releases.}
\resumeItem{Strengthened security and scalability with Trivy/ECR image scans, IAM least-privilege roles, autoscaling, load balancing, and Okta-based authentication integrations.}
\resumeItem{Provisioned AWS lab environments for 250+ attendees by automating database user setup and SFTP access via AWS Transfer Family.}
\resumeItem{\textbf{Tech Stack:} AWS, Terraform, ECS Fargate, Docker, GitHub Actions, Trivy, ECR, IAM, Okta}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
{PEGA}{Dec 2021 -- Oct 2024}
{Software Engineer}{Bengaluru, India}
\resumeItemListStart
\resumeItem{Redesigned CI/CD infrastructure and automated operational workflows, reducing manual intervention and shortening release cycles.}
\resumeItem{Built CloudFormation automation for installing/upgrading Bitbucket and Artifactory, achieving 90\% faster deployments and higher environment reliability.}
\resumeItem{Developed a Bitbucket plugin (Java APIs) to enforce access controls and keep SailPoint permissions in sync, improving audit readiness and compliance.}
\resumeItem{Stabilized a CloudBees Jenkins master by splitting builds across multiple masters using Configuration as Code, improving throughput by 25\%.}
\resumeItem{Delivered an ALMTools Webex bot to automate access/ops requests, reducing request turnaround time.}
\resumeItem{Wrote scripts to extract Kubernetes and cost metrics (e.g., Kubecost) at scale and load them into a data warehouse, improving reporting accuracy and data quality.}
\resumeItem{Built Grafana dashboards and alerts for Kubernetes, AWS nodes, and tooling metrics to reduce troubleshooting time.}
\resumeItem{\textbf{Tech Stack:} AWS, Kubernetes, Docker, Python, Bash, Java, Terraform, Ansible, CI/CD, Grafana}
\resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart
\resumeSubheading
{Red Hat}{June 2021 -- Nov 2021}
{ATSE Intern}{Pune, India}
\resumeItemListStart
\resumeItem{Installed and configured RHEL8, OpenShift, and OpenStack environments; reduced setup time by 40\% via standardized runbooks.}
\resumeItem{Provided troubleshooting support for Red Hat enterprise application platforms and layered products, achieving a 95\% issue resolution rate within SLA.}
\resumeItem{Automated on-demand Kubernetes cluster provisioning on AWS using Terraform + Ansible + shell scripts, reducing provisioning time.}
\resumeItem{\textbf{Tech Stack:} RHEL, OpenShift, OpenStack, AWS, Terraform, Ansible}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Achievements-----------
\section{Achievements}
\resumeSubHeadingListStart
\begin{itemize}[leftmargin=0.15in, topsep=2pt, itemsep=2pt]
\small{
\item Gold Award: 1st place in IDE-India Hackathon at Pegasystems (03/2022).
\item 1st place in inter-year annual technical project event, J-Techtrix (02/2019).
\item Solved 500+ problems across LeetCode, HackerRank, and Codeforces.
}
\end{itemize}
\resumeSubHeadingListEnd

%-----------CERTIFICATIONS---------------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, topsep=2pt, itemsep=2pt]
\small{
\item Red Hat Certified System Administrator (RHEL8) \hfill Red Hat Certified Engineer (RHCE)
\item Oracle Cloud Infrastructure Developer 2020 Certified Associate \hfill AWS Developer -- Udemy
}
\end{itemize}

\end{document}
